---
title: "00_data"
output: html_notebook
---
>!!!! Adjustments needed based on final decision on target variable ->
we need to filter out the TMAs and VLE activities based on the target variable 
date:
 - for final_result keep it as it is
 - for TMAs we need to check day in assessment table to filter the VLE activities
 - for TMAs we need to filter out TMAx where x > y, where TMAy is selected as target variable
TMA ids (in assessment table) are increasing integers so id_assessment of TMA1 
is the smallest value for selected module and presentation

# Init
```{r init, include=FALSE}
library(tidyverse)
library(oulad)
library(patchwork)
library(magrittr)
library(stringr)
```

# General analysis
```{r explore-final-result}
g1 <-
  student %>% 
  select(code_module, code_presentation, final_result) %>%
  mutate(course = paste0(code_module, " ", code_presentation)) %>% 
  group_by(course) %>%
  count() %>%
  ggplot(aes(x = course, y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Course",
       y = "# of students") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

g2 <- 
  student %>% 
  select(code_module, code_presentation, final_result) %>%
  mutate(course = paste0(code_module, " ", code_presentation)) %>% 
  group_by(course) %>% 
  count(final_result) %>%
  mutate(final_result = factor(final_result, labels = c("Distinction",
                                                        "Pass",
                                                        "Fail",
                                                        "Withdrawn")
                               ),
         total_n = sum(n),
         n = n / sum(n)
  ) %>% 
  ggplot(aes(x = course, y = n, fill = final_result)) +
  geom_bar(stat = "identity") +
  labs(x = "Course",
       y = "% of students") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

g1 / g2
```

```{r explore-assessmet-results, fig.width=10, fig.height=20}
student %>% 
  select(code_module, code_presentation, id_student) %>% 
  left_join(student_assessment, by = "id_student") %>%
  left_join(assessment, by = c("code_module", "code_presentation", "id_assessment"))%>%
  filter(assessment_type == "TMA",
         !is_banked,
         date_submitted <= date) %>% 
  mutate(result = ifelse(score >= 40, "Pass", "Fail"),
         result = ifelse(is.na(score), "Fail", result),
         result = factor(result, levels = c("Pass","Fail"))) %>% 
  select(code_module, code_presentation, id_assessment, id_student, result) %>% 
  group_by(code_module, code_presentation) %>% 
  mutate(id_assessment = paste0("TMA", id_assessment-min(id_assessment)+1)) %>% 
  group_by(code_module, code_presentation, id_assessment, result) %>%
  count() %>%
  group_by(code_module, code_presentation, id_assessment) %>%
  mutate(n = n / sum(n)) %>% 
  ggplot(aes(x = id_assessment, y = n, fill = result)) +
  geom_bar(stat = "identity") +
  labs(x = "Assessment",
       y = "# of students") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(code_module~code_presentation, scale = "free", ncol = 2)

```

Based on number of students and the rates I would go for DDD 2013J and DDD 2014J.

# Detailed analysis
```{r detailed-analysis-DDD}
student %>% 
  filter(code_module == "DDD", code_presentation %in% c("2013J","2014J"), final_result != "Withdrawn") %>%
  select(code_module, code_presentation, id_student, final_result) %>%
  mutate(final_result = ifelse(final_result == "Distinction", "Pass", final_result),
         final_result = factor(final_result, levels = c("Pass",
                                                        "Fail")
                               )) %>%
  group_by(code_module, code_presentation) %>% 
  count(final_result) %>% 
  mutate(n = n / sum(n)) %>% 
  ggplot(aes(x = code_presentation, y = n, fill = final_result)) + 
  geom_bar(stat = "identity") +
  labs(title = "Final result distribution for DDD",
       x = "Presentation",
       y = "% of students") +
  theme_classic()
```

```{r detailed-analysis-DDD-assessments}
# filter out all withdrawn
student %>% 
  filter(code_module == "DDD", code_presentation %in% c("2013J","2014J"), final_result != "Withdrawn") %>%
  select(code_module, code_presentation, id_student) %>% 
  left_join(student_assessment, by = "id_student") %>%
  left_join(assessment, by = c("code_module", "code_presentation", "id_assessment"))%>%
  filter(assessment_type == "TMA") %>% 
  mutate(result = ifelse(score >= 40, "Pass", "Fail"),
         result = ifelse(is.na(score), "Fail", result),
         result = factor(result, levels = c("Pass","Fail"))) %>% 
  select(code_module, code_presentation, id_assessment, id_student, result) %>% 
  group_by(code_module, code_presentation) %>% 
  mutate(id_assessment = paste0("TMA", id_assessment-min(id_assessment)+1)) %>% 
  group_by(code_module, code_presentation, id_assessment, result) %>%
  count() %>%
  group_by(code_module, code_presentation, id_assessment) %>%
  mutate(n = n / sum(n)) %>% 
  ggplot(aes(x = id_assessment, y = n, fill = result)) +
  geom_bar(stat = "identity") +
  labs(x = "Assessment",
       y = "% of students") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(code_module~code_presentation, scale = "free", ncol = 2) +
  theme_classic()

```

# Prepare data
```{r prepare-data}
final_dataset <-
  student %>% 
  filter(code_module == "DDD", code_presentation %in% c("2013J","2014J"), final_result != "Withdrawn") %>%
  left_join(student_assessment, by = "id_student") %>%
  left_join(assessment, by = c("code_module", "code_presentation", "id_assessment"))%>%
  filter(assessment_type == "TMA") %>% 
  group_by(code_module, code_presentation) %>% 
  # filter(id_assessment <= <id_assesment-of-selected-TMA>) %>%
  mutate(id_assessment = paste0("TMA", id_assessment-min(id_assessment)+1),
         #result = ifelse(score >= 40, "Pass", "Fail"),
         score = ifelse(is.na(score), 0, score),
         score = ifelse(score > 100, 100, score),
         final_result = ifelse(final_result %in% c("Pass","Distinction"), "Pass", "Fail")
         ) %>% 
  select(code_module, 
         code_presentation,
         id_student,
         gender,
         region,
         highest_education,
         imd_band,
         age_band,
         num_of_prev_attempts,
         studied_credits,
         disability,
         final_result,
         id_assessment,
         score) %>% 
  pivot_wider(names_from = id_assessment,
              values_from = score,
              values_fill = list(score = 0))

final_vle_activity <-
  student_vle %>% 
  filter(code_module == "DDD", code_presentation %in% c("2013J","2014J")) %>% 
  # filter(date < <date-from-assessment-table>) %>% 
  mutate(date1 = if_else(date >= 0, date+1, date),
         week = floor(date1 / 7)) %>% 
  left_join(vle, by = c("code_module","code_presentation","id_site")) %>% 
  select(code_module,
         code_presentation,
         activity_type,
         id_student, week,
         sum_click) %>% 
  group_by(code_module, code_presentation, id_student, activity_type, week) %>%
  summarise(sum_click = sum(sum_click)) %>% 
  arrange(week, code_module, code_presentation, id_student, activity_type) %>% 
  pivot_wider(names_from = c(week, activity_type),
              names_prefix = "week_",
              values_from = sum_click,
              values_fill = list(sum_click = 0))

final_vle_activity %<>%
  semi_join(final_dataset, by = c("code_module","code_presentation","id_student"))

names(final_vle_activity) <- 
  str_replace(names(final_vle_activity),"-","minus_")

final_vle <-
  student_vle %>% 
  filter(code_module == "DDD", code_presentation %in% c("2013J","2014J")) %>% 
  # filter(date < <date-from-assessment-table>) %>% 
  mutate(date1 = if_else(date >= 0, date+1, date),
         week = floor(date1 / 7)) %>% 
  select(code_module,
         code_presentation,
         id_student, week,
         sum_click) %>% 
  group_by(code_module, code_presentation, id_student, week) %>%
  summarise(sum_click = sum(sum_click)) %>% 
  arrange(week, code_module, code_presentation, id_student) %>% 
  pivot_wider(names_from = week,
              names_prefix = "week_",
              values_from = sum_click,
              values_fill = list(sum_click = 0))

final_vle %<>%
  semi_join(final_dataset, by = c("code_module","code_presentation","id_student"))

names(final_vle_activity) <- 
  str_replace(names(final_vle_activity),"-","minus_")

final_dataset %<>%
  semi_join(final_vle, by = c("code_module","code_presentation","id_student"))

final_dataset %>% 
  left_join(final_vle, by = c("code_module","code_presentation","id_student")) %>%
  left_join(final_vle_activity, by = c("code_module","code_presentation","id_student")) %T>%
  write_csv("../output/dataset.csv")

```

